---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library(devtools)
load_all()
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pedstyling

<!-- badges: start -->
<!-- badges: end -->

This package offers styling options with PEDSnet fonts and colors for visualizing and reporting.

## Installation

You can install this package by running the following: 

``` r
devtools::install_github("PEDSnet/pedstyling")
```

## Requirements 

```r
# Uncomment if the following packages are not yet installed
# install.packages(c("ggplot2","sysfonts","showtext"))

library(ggplot2)
library(sysfonts)
library(showtext)

# To load PEDSnet style fonts, only need to include the following lines once at the beginning of your code. 
font_add_google(name = "Lato", family = "lato")
font_add_google(name = "Montserrat", family = "montserrat")
showtext_auto()
```

```{r include=FALSE}
# Uncomment if the following packages are not yet installed
# install.packages(c("ggplot2","sysfonts","showtext"))

library(ggplot2)
library(sysfonts)
library(showtext)

# To load PEDSnet style fonts, only need to include the following lines once at the beginning of your code. 
font_add_google(name = "Lato", family = "lato")
font_add_google(name = "Montserrat", family = "montserrat")
showtext_auto()
```

## Usage

### Descriptive Functions

#### `pedsnet_cols`

Function to extract hex colors from PEDsnet styling palette by name 

```{r}
# Extracting hex and name of all colors in palette  
pedsnet_cols() 

# Extracting hex and name for one color
pedsnet_cols("dark blue", "orange")
```

```R
# Example Usage
ggplot(...) + 
  geom_point(color = pedsnet_cols())

# To pull out specific colors: 
ggplot(...) + 
  geom_point(color = pedsnet_cols("orange"))
```
#### `pedsnet_pal`

Function to access and interpolate palette colors. All possible palettes: 

* 'main' 
* 'dark' 
* 'light' 
* 'mixed' 
* 'light-ish'

It is also possible to expand the color palette based on the original hex codes. This is done by choosing a palette and the number of additional codes to expand to:  

```{r}
# Example
pedsnet_pal("light")(6)
```

```{r echo=FALSE}
library(scales)
pal <- pedsnet_pal("light")(6)
show_col(pal)
```

### Functions to use with ggplot2 

#### `scale_color_pedsnet` 

To specificy color palette when color argument is used

```R
ggplot(dataset, aes(x, y, color = variable)) + 
    scale_color_pedsnet()
    
# To specify a palette 
ggplot(dataset, aes(x, y, color = variable)) + 
    scale_color_pedsnet(discrete = FALSE, palette = "light-ish")
```

```{r include=FALSE}
library(ggplot2)
library(dplyr)

df <- data.frame(X = sample(1:30, 50, replace = TRUE),
                 Y = sample(1:100, 50, replace = TRUE)) %>% 
  mutate(Category_X = case_when(X < 15 ~ "< 15",
                                TRUE ~ "> 15"))
```

```{r}
# Example Plot with Stying
ggplot(df, aes(X, Y)) +
  geom_point(color=pedsnet_cols("orange")) + 
  theme_pedsnet() +
  labs(title = "This is a test",
       caption = "This is a caption test.")
```


#### `scale_fill_pedsnet` 

To specificy color palette when fill argument is used:

```R
ggplot(dataset, aes(x, y, fill = variable)) + 
    scale_fill_pedsnet()
    
# To specify a palette 
ggplot(dataset, aes(x, y, fill = variable)) + 
    scale_fill_pedsnet(palette = "light")
```

```{r}
# Example Plot with Stying
ggplot(df, aes(X, Y, fill=Category_X)) +
  geom_bar(stat="identity") +
  scale_fill_pedsnet("mixed") +
  theme_pedsnet() +
  labs(title = "This is a test",
       caption = "This is a caption test.")
```

<small><i>This package was created using the following tutorial: [Creating corporate colour palettes for ggplot2](https://drsimonj.svbtle.com/creating-corporate-colour-palettes-for-ggplot2)


 

